Results

### 2024-03-07 Model/htw_model.qmd
combined results. Model deviation predictions. More hybrid fits.

@@

>>>>

post_dat_l <- post_dat_l |> mutate(dist = case_when(
    val >= x & val <= x + 200 ~ 0,                 
    val < x ~ abs(x - val),                       
    val > x + 200 ~ abs(val - (x + 200)),           
    TRUE ~ NA_real_                                 
  ))

@@

## Deviation Predictions

```{r}
#| fig-height: 12
#| fig-width: 11
 post_dat_l |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=condit,y=dist,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~Resp, axes = "all",ncol=3,scale="free")

### 2024-03-07 Model/htw_model_e2.qmd
combined results. Model deviation predictions. More hybrid fits.

# organize test data predictions
 post_dat <- nestSbjModelFit |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
    generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 50, return_dat="test_data")
    })) |> 
   select(Fit_Method,pp,-data) |>  
   unnest(pp) |>  filter(expMode2=="Test") |> as.data.table()
# 
# saveRDS(post_dat, here("data/model_cache/post_dat.rds"))

#post_dat <- readRDS(here("data/model_cache/post_dat.rds"))

>>>>

#  post_dat <- nestSbjModelFit |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
#     generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 50, return_dat="test_data")
#     })) |> 
#    select(Fit_Method,pp,-data) |>  
#    unnest(pp) |>  filter(expMode2=="Test") |> as.data.table()

# saveRDS(post_dat, here("data/model_cache/post_dat_e2.rds"))

post_dat <- readRDS(here("data/model_cache/post_dat_e2.rds"))

### 2024-03-07 Model/htw_model_e3.qmd
combined results. Model deviation predictions. More hybrid fits.

# organize test data predictions
 post_dat <- nestSbjModelFit |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
    generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 30, return_dat="test_data")
    })) |> 
   select(Fit_Method,pp,-data) |>  
   unnest(pp) |>  filter(expMode2=="Test") |> as.data.table()
# 
# saveRDS(post_dat, here("data/model_cache/post_dat.rds"))

#post_dat <- readRDS(here("data/model_cache/post_dat.rds"))

@@

# organize training data predictions
 pd_train <- nestSbjModelFit |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
   generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 20, return_dat="train_data")
    })) |>
   select(Fit_Method,pp,-data) |>
  unnest(pp) |> as.data.table() |> filter(expMode2=="Train")

#saveRDS(pd_train, here("data/model_cache/pd_train.rds"))

#pd_train <- readRDS(here("data/model_cache/pd_train.rds"))

@@

>>>>

# organize test data predictions
#  post_dat <- nestSbjModelFit |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
#     generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 50, return_dat="test_data")
#     })) |> 
#    select(Fit_Method,pp,-data) |>  
#    unnest(pp) |>  filter(expMode2=="Test") |> as.data.table()
# 
#saveRDS(post_dat, here("data/model_cache/post_dat_e3.rds"))

post_dat <- readRDS(here("data/model_cache/post_dat_e3.rds"))

@@

post_dat_l <- post_dat_l |> mutate(dist = case_when(
    val >= x & val <= x + 200 ~ 0,                 
    val < x ~ abs(x - val),                       
    val > x + 200 ~ abs(val - (x + 200)),           
    TRUE ~ NA_real_                                 
  ))

# organize training data predictions
#  pd_train <- nestSbjModelFit |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
#    generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 20, return_dat="train_data")
#     })) |>
#    select(Fit_Method,pp,-data) |>
#   unnest(pp) |> as.data.table() |> filter(expMode2=="Train")

#saveRDS(pd_train, here("data/model_cache/pd_train_e3.rds"))

pd_train <- readRDS(here("data/model_cache/pd_train.rds"))

@@

## Deviation Predictions

```{r}
#| fig-height: 11
#| fig-width: 11
 post_dat_l |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=condit,y=dist,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~Resp, axes = "all",ncol=3,scale="free")

```{r}
#| fig-height: 16
#| fig-width: 12
 po <- post_dat_l |> 
  filter(bandOrder=="Original") |>
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=condit,y=dist,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~Resp, axes = "all",ncol=3,scale="free")+
  labs(title="Original Order")

  pr <- post_dat_l |> 
  filter(bandOrder=="Reverse") |>
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvg$vb))) |>
  ggplot(aes(x=condit,y=dist,fill=vbLab)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~Resp, axes = "all",ncol=3,scale="free")+
  labs(title="Reverse Order")

  po/pr

### 2024-03-07 Sections/Intro.qmd
combined results. Model deviation predictions. More hybrid fits.

The influence of variability on function learning tasks has received relatively little attention.  @deloshExtrapolationSineQua1997 did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs (with the total number of training trials held constant). They found a minimal influence of variability on training performance, and no difference between groups in extrapolation.

@vandamMappingShapeVisuomotor2015 employed a visuomotor function learning task which required participants to learn a linear relationship between an input shape (which ranged continuously from very spiky to completely circular) and the correct pointing position.

>>>>

The influence of variability on function learning tasks has received relatively little attention.  The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant. They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.

In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response. The shapes ranged from very spiky to completely circular at the extreme ends of the space. Participants trained with intermediate shapes from a lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower varied condition matching the items used on the extreme ends of the higher variation training space. Learning was significantly slower in the higher variation group. However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitudes to the most similar training item, rather than in accordance with the true linear function.  The authors accounted for both learning and extrapolation performance with a Bayesian learning model. Similar to ALM, the bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli. However unlike ALM, the bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
